\paragraph{Minutes 14.09.2009}  
The meeting took place at 1:30pm on the above date. The meeting location was in the computer science atrium. 

\paragraph{Present}

\begin{itemize}
	\item Julie Greensmith (\textbf{Supervisor})
	\item Amy (\textbf{Chair})
	\item Dhruv (\textbf{Minutes Taker})
	\item Jue
	\item Rob
	\item Chris 
\end{itemize}

\paragraph{Tasks completed}

\begin{enumerate}
	\item Elect group leader
	\item System Specifications- Done, consented by Dr Greensmith
	\item Collaborate using Base Camp.
	\item Dr Greensmith joined the Base Camp network.
\end{enumerate}


\paragraph{Issues discussed}

\begin{itemize}
	\item Django doesn’t seem like cheating- its just reusing what is available. Plus, clients just want to see the functioning product. Focus isn’t on how you’ve made it.
	
	\item Ideally, develop a Facebook application along with the website. Add to ideal column in specification list.
	
	\item How do you get a massive userbase?
	
	\item Dr Greensmith endorses the realistic level of the specification as a good target.
	
	\item Ideal level of specification will be a great achievement, results can possibly be published.
	
	\item Binary matching of ingredients to recipes of specific type? There exists technology to support such a venture.
	
	\item Input from machine learning + user feedback, as a combination.
	
	\item Crowdsourcing technology.
	
	\item Quality of interface separates the minimum specification level from the realistic level.
	
	\item Ideal list-- Has a full user system with profiles and user-uploaded recipes—seems hare to do.
	
	\item How to measure extent of collaboration? Comparing the size of the userbase? 
	
	\item Collaborative filtering?
	
	\item Ideal list-- Gives recipe recommendations for several users i.e. ‘A recipe that alice and bob will both like’. Hard to do but its an awesome goal!
	
	\item Gantt charts are not as useful as Milestone markers.
	
	\item Identify end points and how to get there.
	
	\item The more you document, the easier to write up later.
	
	\item Keep a progress log.
	
	\item Design decisions need to be justified.
	
	\item Seems like everything needs to be justified.
	
	\item Set up blog?
	
	\item Focus on good planning.
	
	\item Have a backup plan.	
\end{itemize}

\paragraph{To do}

\begin{enumerate}
	\item Milestone markers
	\item Ideas for what the prototype is going to look like.
	\item Assigning leadership roles for specific areas.
	\item Decide on using Django?
	
\end{enumerate}

