\textbf{G52GRP- Digital Chef} \\

\textbf{Date-} 14/09/09 \textbf{People Present-} Everyone.
\textbf{Minutes taker-} Dhruv Gairola \\

\textbf{Tasks Done}

Elect group leader- Amy

System Specifications- Done, consented by Dr Julie Greensmith

Collaborate using Base Camp.

Dr Greensmith joined Base Camp network. \\

\textbf{Discussion}

\begin{itemize}
\item
  Django doesn’t seem like cheating- its just reusing what is
  available. Plus, clients just want to see the functioning product.
  Focus isn’t on how you’ve made it.
\item
  Ideally, develop a Facebook application along with the website. Add
  to ideal column in specification list.
\item
  How do you get a massive userbase?
\item
  Dr Greensmith endorses the realistic level of the specification as
  a good target.
\item
  Ideal level of specification will be a great achievement, results
  can possibly be published.
\item
  Binary matching of ingredients to recipes of specific type? There
  exists technology to support such a venture.
\item
  Input from machine learning + user feedback, as a combination.
\item
  Crowdsourcing technology.
\item
  Quality of interface separates the minimum specification level from
  the realistic level.
\item
  Ideal list-- Has a full user system with profiles and user-uploaded
  recipes—seems hare to do.
\item
  How to measure extent of collaboration? Comparing the size of the
  userbase?
\item
  Collaborative filtering?
\item
  Ideal list-- Gives recipe recommendations for several users i.e. ‘A
  recipe that alice and bob will both like’. Hard to do but its an
  awesome goal!
\item
  Gantt charts are not as useful as Milestone markers.
\item
  Identify end points and how to get there.
\item
  The more you document, the easier to write up later.
\item
  Chris shows interest in documentation!
\item
  Keep a progress log.
\item
  Design decisions need to be justified.
\item
  Seems like everything needs to be justified.
\item
  Set up blog?
\item
  Focus on good planning.
\item
  Have a backup plan.
\end{itemize}
\\
\textbf{To Do}

Milestone markers

Ideas for what the prototype is going to look like.

Assigning leadership roles for specific areas.

Decide on using Django?

