\documentclass[12pt]{article}


                    % used by \maketitle


\setlength{\topmargin}{-.4in}
\setlength{\textheight}{9in}
\setlength{\oddsidemargin}{.125in}
\setlength{\textwidth}{6.25in}

\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
  {-3.25ex\@plus -1ex \@minus -.2ex}%
  {1.5ex \@plus .2ex}%
  {\normalfont\normalsize\bfseries}}
\makeatother

\begin{document}
\paragraph{Minutes 07.10.2009}  
The meeting took place at 1:30pm on the above date. The meeting location was in the computer science atrium. 

\paragraph{Present}

\begin{itemize}
	\item Julie Greensmith (\textbf{Supervisor})
	\item Dhruv (\textbf{Chair})
	\item Amy (\textbf{Minute Taker})
	\item Jue
	\item Rob
	\item Chris 
	
\end{itemize}

\paragraph{Issues discussed}

\begin{itemize}
	\item To gain trust as a group and communicate.
	\item Relationship with Julie Greensmith is client based. 
	\item Julie is passionate about cooking and finds that the BBC website is very limited as it only allows you to input 3 ingredients.
	\item Perhaps make the software portable.
	\item Focus on functionality, but ensure you have a good GUI. 
	\item By Christmas we should be delivering a prototype, which is basic (build onto this).
	\item Make the software “not just a database website”. Include collaborative filtering - users, profiles, preferences, community based approach. This will give the software the WOW factor!
	\item Aims have to be achievable.
	
\end{itemize}

\paragraph{To do}

\begin{enumerate}
	\item Complete a specification before the next formal meeting.
\end{enumerate}



\end{document}             % End of document.